---
title: "Homework 1"
author: "Yuqi Wang"
date: "9/14/2020"
output: html_document
---

This is my solution to Homework 1.

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements.

```{r create_df}
problem1_df <- tibble(
  random_num = rnorm(n = 10),
  logic_vec = random_num > 0,
  char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vec = factor(c("low", "low", "low", "mid", "mid", "mid", "high", "high", "high", "low"))
)

problem1_df
```


Next, we take the mean of the four columns in the data frame.

```{r pull_mean}
mean(pull(problem1_df, random_num))
mean(pull(problem1_df, logic_vec))
mean(pull(problem1_df, char_vec))
mean(pull(problem1_df, factor_vec))
```

The results of the mean function shows that the mean of numeric variable and logic vector can be calculated, while character vector and factor vector do not work.

Using `as.numeric` function to convert variable type:

```{r change_type, eval=FALSE}
as.numeric(pull(problem1_df, random_num))
as.numeric(pull(problem1_df, logic_vec))
as.numeric(pull(problem1_df, char_vec))
as.numeric(pull(problem1_df, factor_vec))
```

The result of `as.numeric` shows that logical vector and factor vector can be converted to numeric variables, while character vector can not been converted. This helps to explain that we can take the mean of the logical vector, but for factor vector, we can not calculate the mean because of its character feature.


The following are the calculations for variable type conversion and the product with the random sample:

```{r calculation}
as.numeric(pull(problem1_df, logic_vec)) * pull(problem1_df, random_num)
as.factor(pull(problem1_df, logic_vec)) * pull(problem1_df, random_num)
as.numeric(as.factor(pull(problem1_df, logic_vec))) * pull(problem1_df, random_num)
```

The result shows that factor vector cannot be used for calculation.

## Problem 2

```{r}
data("penguins", package = "palmerpenguins")
```

Description of the `penguins` dataset:

* The `penguins` data set collected data for penguins of the following species: `r unique(penguins$species)`. These penguins were from `r unique(penguins$island)` and the data was collected for year `r unique(penguins$year)`. The data set contains variables including `r ls(penguins)`.

  * The maximum of bill length is `r max(penguins$bill_length_mm, na.rm = TRUE)` mm, the minimum of bill length is `r min(penguins$bill_length_mm, na.rm = TRUE)` mm, and the mean is `r mean(penguins$bill_length_mm, na.rm = TRUE)` mm.

  * The maximum of bill depth is `r max(penguins$bill_depth_mm, na.rm = TRUE)` mm, the minimum of bill depth is `r min(penguins$bill_depth_mm, na.rm = TRUE)` mm, and the mean is `r mean(penguins$bill_depth_mm, na.rm = TRUE)` mm.

  * The maximum of flipper length is `r max(penguins$flipper_length_mm, na.rm = TRUE)` mm, the minimum of bill depth is `r min(penguins$flipper_length_mm, na.rm = TRUE)` mm.

  * The maximum of body mass is `r max(penguins$body_mass_g, na.rm = TRUE)` g, the minimum of bill depth is `r min(penguins$body_mass_g, na.rm = TRUE)` g, and the mean is `r mean(penguins$body_mass_g, na.rm = TRUE)` g.

  * The numbers of female, male and sex-unspecified penguins are `r summary(penguins$sex)`.

* The `penguins` data set includes `r ncol(penguins)` variables to describe the characteristics for `r nrow(penguins)` observations. 

* The mean flipper length is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), digits = 2)` mm. 

#### Scatterplot

```{r}
# build the scatterplot between bill length and flipper length
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

# save the plot to the project directory
ggsave("penguin.pdf", height = 5, width = 4)
```
